A survey of HTTP caching options on the open Web

### 2015-01-14 sanity/paper1.tex
Some proofreading; some more on related work
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@979 43ef1190-90fd-4dd7-a769-d0121f02b80e

In spite of this, we have not seen it in widespread use in the
Semantic Web, and therefore we decided to conduct a survey to
investigate the actual compliance to RFC7234 and RFC7232. Our reasons
to do this include\todo{formulate as contributions?}
\begin{enumerate}
\item Understand the actual usage rather than rely on anecdotal
  conceptions.
\item Encourage the implementation of these mechanisms in Semantic Web
  infrastructure.
\item Point out future research directions.
\end{enumerate}

@@

Caching, as defined in RFC7234, requires that the server declares how
long into the future it expects the information resource in the
response to remain fresh, i.e. how long it is permissible to use
it. Based on this, the client need not contact the server at all to
reuse a cached response, but this requires a commitment from the
content provider. The standard also gives the client an opportunity to
heuristically determine a time to live. RFC7232, on the other hand,
defines a protocol for asking the server if the cached response is
still fresh using conditional requests. This doesn't burden the
content provider with the task of estimating the time to live
beforehand, but then, it must be able to answer if the resource has
changed less expensively than serving the entire response. These two
approaches can be combined, as a client may ask if a response is fresh
after it has expired.

@@

Key contributions of this paper are:\todo{write}

@@

The \cite{dyldo2} Dynamic Linked Data Observatory (DyLDO)
performed, and continue to do so, of parts of the Linked Open Data
Cloud to determine dynamicity characteristics of Linked Data. Caching
is one of their motivations, but they have not published statistics on
HTTP headers.

@@

In the broader Web literature, \cite{ager2010revisiting} analysed the
value of caching based anonymized traces of actual Web usage at a
major Internet Service Provider.

>>>>

In spite of this, we have not seen it in widespread use in the
Semantic Web, and therefore we decided to conduct a survey to
investigate the actual compliance to RFC7234 and RFC7232. 
With this paper, we hope to achieve the following:
\begin{enumerate}
\item Understand the actual usage rather than rely on anecdotal
  conceptions.
\item Encourage the implementation of these mechanisms in Semantic Web
  infrastructure.
\item Point out future research directions.
\end{enumerate}

@@

Caching, as defined in RFC7234, requires that the server declares how
long into the future it expects the information resource in the
response to remain fresh, i.e. how long it is permissible to use
it. Based on this, the client doesn't need to contact the server at
all to reuse a cached response, but this requires a commitment from
the content provider. The standard also gives the client an
opportunity to heuristically determine a time to live. RFC7232, on the
other hand, defines a protocol for asking the server if the cached
response is still fresh using conditional requests. This doesn't
burden the content provider with the task of estimating the time to
live beforehand, but then, it must be able to answer if the resource
has changed less expensively than serving the entire response. These
two approaches can be combined, as a client may ask if a response is
fresh after it has expired. A number of headers are relevant to the
problem, we recorded those in Table~\ref{tab:headers} in
Appendix~\ref{app:fetcher} but they were not all used in this analysis.

@@

@@

The \cite{dyldo2} Dynamic Linked Data Observatory (DyLDO) performed,
and continue to do so, monitoring of parts of the Linked Open Data
Cloud to determine dynamicity characteristics of Linked Data. Caching
is one of their motivations, but they have not published statistics on
HTTP headers.

@@

In the broader Web literature, \cite{ager2010revisiting} analysed the
value of caching based anonymized traces of actual Web usage at a
major Internet Service Provider. They find that while caching often
yields little benefit when content is user-generated, they still find
some potential.

While these studies have little overlap with the present paper, they
underline the importance of understanding the current deployment and
future potential. In some of the related work, it is shown that
caching does not necessarily give tanglible benefits. Yet, we shall
assume that sharing the metadata required for caching outside of the
server is desireable, and that it is possible in most cases. We shall
see that it most likely will be beneficial in cases that do not
benefit from caching today.
